---
title: "Faster conversion from sf to WKT"
output:
  html_document:
    df_print: paged
---

**
The [lwgeom](https://cran.r-project.org/web/packages/lwgeom/index.html) package
and the use of the global `Sys.setenv("LWGEOM_WKT" = "true")` option allows
faster conversion of *simple features* objects to well-known text (WKT)
representation, due to the use of low-level code. It also enables faster
printing of complex geometries. Note that using this method, the output may
differ from the default, which can cause reproducibility problems.
**

**
Alternatively, you can also use the
[lwgeom::st_astext()](https://r-spatial.github.io/lwgeom/reference/st_astext.html)
and [wk::as_wkt()](https://paleolimbot.github.io/wk/reference/wkt.html)
functions directly.
**

<details>
<summary>Code</summary>

```{r message=FALSE}
library("sf")
```

```{r}
# generate some data
n = 100000
pts = data.frame(x = rnorm(n), y = rnorm(n))
pts = st_as_sf(pts, coords = c("x", "y"))
pts = st_as_sfc(pts)
```

```{r}
system.time(x <- st_as_text(pts))
x[1]
```

```{r}
# `lwgeom` must be installed
Sys.setenv("LWGEOM_WKT" = "true")
system.time(y <- st_as_text(pts))
y[1]
```

</details>
